Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media

### 2018-01-19 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

\medskip
The displacement efficiency depends upon the ratio of the viscous to capillary forces or capillary number ($N_{c}$, see eq.\ref{eq:capillary_number}). 
%Flow instabilities will occur due to: pressure gradient along the interface of fluids; stress forces acting in opposite directions; mobility differences that may exceed critical limits and; heterogeneities of the domain (layering). 
When viscous force of the injected fluid overcomes the capillary force, hydrodynamic instabilities may occur, resulting in the collapse of the interface between fluids and start forming fingers.

@@

\medskip
In the next section \ref{section:results_setup} is an introduction to the model that will be used followed by section \ref{section:results_initial_model_validation} will be discussed. Multi-fluid simulations are performed to numerically investigate (a) the impact of heterogeneity (here represented by spatially-dependent permeability) on the onset and propagation of viscous instabilities (Sections \ref{section:results_homo_hete}-\ref{section:results_hete_fix_adapt}) (b) flow pathways in 3D heterogeneous systems (Section \ref{section:results_3D}).

>>>>

\medskip
The efficiency of fluid displacement depends upon the ratio of viscous and capillary forces (or capillary number, $N_{c}$, Eqn.~\ref{eq:capillary_number}). 
%Flow instabilities will occur due to: pressure gradient along the interface of fluids; stress forces acting in opposite directions; mobility differences that may exceed critical limits and; heterogeneities of the domain (layering). 
When viscous force of the injected fluid overcomes the capillary force, hydrodynamic instabilities may occur, resulting in the collapse of the interface between fluids and start forming fingers.

@@

\medskip
In the next section \ref{section:results_setup} is an introduction to the model that will be used followed by section \ref{section:results_initial_model_validation} will be discussed. Multi-fluid simulations are performed to numerically investigate (a) the impact of heterogeneity (here represented by spatially-dependent permeability) on the onset and propagation of viscous instabilities (Sections \ref{section:results_homo_hete}-\ref{section:results_hete_fix_adapt}) (b) flow pathways in 3D heterogeneous systems (Section \ref{section:results_3D}). \red{KOSTAS, please read and rewrite this paragraph!}
